GSE158422: DNA methylation in Lung squamous cell carcinoma

### 2023-12-21 figs/GSE158422.Rmd
fix source path
increase dl timeout
fix timeout

source("../meth_functions.R")

@@

ARRAY_DATA="GSE158422_RAW.tar"
if(!file.exists(ARRAY_DATA)){
  download.file("https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE158422&format=file",
    destfile=ARRAY_DATA)
  untar(tarfile = ARRAY_DATA)
}

SERIES_MATRIX="GSE158422_series_matrix.txt.gz"
if(!file.exists(SERIES_MATRIX)){
download.file("https://ftp.ncbi.nlm.nih.gov/geo/series/GSE158nnn/GSE158422/matrix/GSE158422_series_matrix.txt.gz",
  destfile=SERIES_MATRIX)
}
gse <- getGEO(filename=SERIES_MATRIX)
baseDir <- "IDAT"
sample_metadata <- pData(phenoData(gse))
sample_metadata$patient <- factor(sapply(strsplit(sample_metadata$title,"_"),"[[",1))

>>>>

source("meth_functions.R")

@@

ARRAY_DATA="GSE158422_RAW.tar"
if(!file.exists(ARRAY_DATA)){
  options(timeout=10000000000000)
  download.file("https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE158422&format=file",
    destfile=ARRAY_DATA)
  untar(tarfile = ARRAY_DATA)
}

SERIES_MATRIX="GSE158422_series_matrix.txt.gz"
if(!file.exists(SERIES_MATRIX)){
  options(timeout=10000000000000)
  download.file("https://ftp.ncbi.nlm.nih.gov/geo/series/GSE158nnn/GSE158422/matrix/GSE158422_series_matrix.txt.gz",
    destfile=SERIES_MATRIX)
}
gse <- getGEO(filename=SERIES_MATRIX)
baseDir <- "IDAT"
sample_metadata <- pData(phenoData(gse))
sample_metadata$patient <- factor(sapply(strsplit(sample_metadata$title,"_"),"[[",1))
